---
title: "Rmarkdown Styling Refernce for myself"
author: "Taehoon Ha"
date: 11/30/2018
output: 
    github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.align = 'center')
```

### Choose Output
Write YAML header that explains what thype of document to build from your R markdown file.

| Output command          | Output type               | 
|-------------------------|---------------------------| 
| `html_document`         | HTML file (web page)      | 
| `pdf_document`          | pdf document              | 
| `word_document`         | Microsoft word document   | 
| `beamer_presentation`   | beamer slideshow (pdf)    | 
| `ioslides_presentation` | ioslides slideshow (html) | 

<br><br><br><br>

### Basic grammar
```{r echo = FALSE}
df <- data.frame(Option = c(
    "horizontal rule (or slide break)",
    "endash",
    "emdash",
    "image",
    "link"), Command = c("***",
                         "--",
                         "---",
                         "`![](directory)`",
                         "`[](web address)`"))

knitr::kable(df)
```

<br><br><br><br>

### Customize R code chunks

| Option             | Display Code | Run Code | Display Result | 
|--------------------|--------------|----------|----------------| 
| `echo = FALSE`     | No           | Yes      | Yes            | 
| `eval = FALSE`     | Yes          | No       | No             | 
| `results = 'hide'` | Yes          | Yes      | No             | 


+ `message = FALSE`: to remove a message in the output after a chunk is executed.
+ `warning = FALSE`: to remove only warning message in the output.
+ `error = FALSE`: to remove the error message in the output.
+ `tidy = TRUE`: reformat code in a tidy way when displaying it
+ `results =`: results "markup" "markup", "asis", "hold", or "hide"
+ `comment = "##"` : Comment character to preface results with
+ Control the size of the figures
    + `fig.height = ` 
    + `fig.width = `
