---
title: "Import Data in R (DB)"
author: "Taehoon Ha"
output: 
    github_document:
        toc: true
        toc_depth: 3
        toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

## Establish a connection
The first step to import data from a SQL database is creating a connection to it. As Filip explained, you need different packages depending on the database you want to connect to. All of these packages do this in a uniform way, as specified in the DBI package.

+ `dbConnect()` creates a connection between your R session and a SQL database. The first argument has to be a DBIdriver object, that specifies how connections are made and how data is mapped between R and the database. Specifically for MySQL databases, you can build such a driver with `RMySQL::MySQL()`.

If the MySQL database is a remote database hosted on a server, you'll also have to specify the following arguments in `dbConnect()`: `dbname`, `host`, `port`, `user` and `password`. Most of these details have already been provided.

```{r}
# Load the DBI package
library(DBI)

# Edit dbConnect() call
con <- dbConnect(RMySQL::MySQL(), 
                 dbname = "tweater", 
                 host =  "courses.csrrinzqubik.us-east-1.rds.amazonaws.com", 
                 port = 3306,
                 user = "student",
                 password = "datacamp")
```

## List the database tables
After you've successfully connected to a remote MySQL database, the next step is to see what tables the database contains. You can do this with the `dbListTables()` function. As you might remember from the video, this function requires the connection object as an input, and outputs a character vector with the table names.

```{r}
# Build a vector of table names: tables
tables <- dbListTables(con)

# Display structure of tables
str(tables)

# Import the users table from tweater: users
users <- con %>% dbReadTable('users')

# Print users
users

# Get table names
table_names <- dbListTables(con)

# Import all tables
tables <- lapply(table_names, dbReadTable, conn = con)

# Print out tables
tables
```






```{r}
# Import tweat_id column of comments where user_id is 1: elisabeth
elisabeth <- dbGetQuery(con, 
                        "SELECT tweat_id
                        FROM comments
                        WHERE user_id = 1")

# Print elisabeth
elisabeth

# Import post column of tweats where date is higher than '2015-09-21': latest
latest <- dbGetQuery(con, "
                     select post
                     from tweats
                     where date > '2015-09-21'")

# Print latest
latest

# Create data frame specific
specific <- dbGetQuery(con, "
                       select message
                       from comments
                       where tweat_id = 77 and user_id > 4")

# Print specific
specific

# Create data frame short
short <- dbGetQuery(con, "
                    select id, name
                    from users
                    where CHAR_LENGTH(name) < 5")

# Print short
short
```

```{r}
# Send query to the database
res <- dbSendQuery(con, "
                   SELECT * 
                   FROM comments 
                   WHERE user_id > 4")

# Use dbFetch() twice
dbFetch(res, 2)
dbFetch(res, 2)

# Clear res
dbClearResult(res)

# Create the data frame  long_tweats
long_tweats <- dbGetQuery(con, "
                          select post, date
                          from tweats
                          where CHAR_LENGTH(post) > 40")

# Print long_tweats
print(long_tweats)

# Disconnect from the database
dbDisconnect(con)
```

```{r}
library(readr)

# Import the csv file: pools
url_csv <- "http://s3.amazonaws.com/assets.datacamp.com/production/course_1478/datasets/swimming_pools.csv"

# Import the txt file: potatoes
url_delim <- "http://s3.amazonaws.com/assets.datacamp.com/production/course_1478/datasets/potatoes.txt"

pools <- read_csv(url_csv)
potatoes <- read_tsv(url_delim)
```

```{r}
# https URL to the swimming_pools csv file.
url_csv <- "https://s3.amazonaws.com/assets.datacamp.com/production/course_1478/datasets/swimming_pools.csv"

# Import the file using read.csv(): pools1
pools1 <- read.csv(url_csv)

# Load the readr package
library(readr)

# Import the file using read_csv(): pools2
pools2 <- read_csv(url_csv)

# Print the structure of pools1 and pools2
str(pools1)
str(pools2)
```

```{r}
# Load the readxl and gdata package
library(readxl)
library(gdata)

# Specification of url: url_xls
url_xls <- "http://s3.amazonaws.com/assets.datacamp.com/production/course_1478/datasets/latitude.xls"

# Import the .xls file with gdata: excel_gdata
excel_gdata <- read.xls(url_xls)

# Download file behind URL, name it local_latitude.xls
#download.file(url_xls, "local_latitude.xls")

# Import the local .xls file with readxl: excel_readxl
excel_readxl <- read_excel("local_latitude.xls")
```

```{r}
# https URL to the wine RData file.
url_rdata <- "https://s3.amazonaws.com/assets.datacamp.com/production/course_1478/datasets/wine.RData"

# Download the wine file to your working directory
download.file(url_rdata, "wine_local.RData")

# Load the wine data into your workspace using load()
load('wine_local.RData')

# Print out the summary of the wine data
summary(wine)
```

```{r}
# Load the httr package
library(httr)

# Get the url, save response to resp
url <- "http://www.example.com/"

# Print resp
resp <- GET(url)
resp

# Get the raw content of resp: raw_content
raw_content <- content(resp, as = "raw")

# Print the head of raw_content
print(raw_content)
```

```{r}
# httr is already loaded

# Get the url
url <- "http://www.omdbapi.com/?apikey=ff21610b&t=Annie+Hall&y=&plot=short&r=json"
resp <- GET(url)

# Print resp
resp

# Print content of resp as text
content(resp, as = "text")

# Print content of resp
content(resp)
```

```{r}
# Load the jsonlite package
library(jsonlite)

# wine_json is a JSON
wine_json <- '{"name":"Chateau Migraine", "year":1997, "alcohol_pct":12.4, "color":"red", "awarded":false}'

# Convert wine_json into a list: wine
wine <- fromJSON(wine_json)

# Print structure of wine
str(wine)
```

```{r}
# jsonlite is preloaded

# Definition of quandl_url
quandl_url <- "https://www.quandl.com/api/v3/datasets/WIKI/FB/data.json?auth_token=i83asDsiWUUyfoypkgMz"

# Import Quandl data: quandl_data
quandl_data <- fromJSON(quandl_url)

# Print structure of quandl_data
str(quandl_data)
```

```{r}
# The package jsonlite is already loaded

# Definition of the URLs
url_sw4 <- "http://www.omdbapi.com/?apikey=ff21610b&i=tt0076759&r=json"
url_sw3 <- "http://www.omdbapi.com/?apikey=ff21610b&i=tt0121766&r=json"

# Import two URLs with fromJSON(): sw4 and sw3
sw4 <- fromJSON(url_sw4)
sw3 <- fromJSON(url_sw3)

# Print out the Title element of both lists
sw4$Title
sw3$Title

# Is the release year of sw4 later than sw3?
sw4$Year > sw3$Year
```

```{r}
# jsonlite is already loaded

# Challenge 1
json1 <- '[1, 2, 3, 4, 5, 6]'
fromJSON(json1)

# Challenge 2
json2 <- '{"a": [1, 2, 3], "b": [4, 5, 6]}'
fromJSON(json2)

# jsonlite is already loaded

# Challenge 1
json1 <- '[[1, 2], [3, 4], [5, 6]]'
fromJSON(json1)

# Challenge 2
json2 <- '[{"a": 1, "b": 2}, {"a": 3, "b": 4}, {"a": 5, "b": 6}]'
fromJSON(json2)
```

```{r}
# jsonlite is already loaded

# URL pointing to the .csv file
url_csv <- "http://s3.amazonaws.com/assets.datacamp.com/production/course_1478/datasets/water.csv"

# Import the .csv file located at url_csv
water <- read.csv(url_csv, stringsAsFactors=F)
str(water)

# Convert the data file according to the requirements
water_json <- toJSON(water)

# Print out water_json
water_json
```

```{r}
# jsonlite is already loaded

# Convert mtcars to a pretty JSON: pretty_json
pretty_json <- toJSON(mtcars, pretty=T)

# Print pretty_json
pretty_json

# Minify pretty_json: mini_json
mini_json <- minify(pretty_json)

# Print mini_json
mini_json
```

```{r}
# Load the haven package
library(haven)

# Import sales.sas7bdat: sales
sales <- read_sas("sales.sas7bdat")

# Display the structure of sales
str(sales)
```

```{r}
# haven is already loaded

# Import the data from the URL: sugar
sugar <- read_dta('http://assets.datacamp.com/production/course_1478/datasets/trade.dta')

# Structure of sugar
str(sugar)

# Convert values in Date column to dates
sugar$Date <- as.Date(as_factor(sugar$Date))

# Structure of sugar again
str(sugar)
```

```{r}
# haven is already loaded

# Import person.sav: traits
traits <- read_sav('http://assets.datacamp.com/production/course_1478/datasets/person.sav')

# Summarize traits
summary(traits)

# Print out a subset
# Print out a subset
subset(traits,
  subset = Extroversion > 40 & Agreeableness > 40)
```

```{r}
# Import SPSS data from the URL: work
work <- read_sav('http://s3.amazonaws.com/assets.datacamp.com/production/course_1478/datasets/employee.sav')

# Display summary of work$GENDER
summary(work$GENDER)

# Convert work$GENDER to a factor
work$GENDER <- as_factor(work$GENDER)

# Display summary of work$GENDER again
summary(work$GENDER)
```

```{r}
# Load the foreign package
library(foreign)

# Import florida.dta and name the resulting data frame florida
florida <- read.dta('http://s3.amazonaws.com/assets.datacamp.com/production/course_1478/datasets/florida.dta')

# Check tail() of florida
tail(florida)

```

```{r}
# foreign is already loaded

# Specify the file path using file.path(): path
path <- file.path("worldbank", 'edequality.dta')

# Create and print structure of edu_equal_1
edu_equal_1 <- read.dta(path)
str(edu_equal_1)

# Create and print structure of edu_equal_2
edu_equal_2 <- read.dta(path, convert.factors=F)
str(edu_equal_2)

# Create and print structure of edu_equal_3
edu_equal_3 <- read.dta(path, convert.underscore=T)
str(edu_equal_3)

```

```{r}
# foreign is already loaded

# Import international.sav as a data frame: demo
demo <- read.spss('http://s3.amazonaws.com/assets.datacamp.com/production/course_1478/datasets/international.sav', to.data.frame=T)

# Create boxplot of gdp variable of demo
boxplot(demo$gdp)
```

```{r}
path <- 'http://s3.amazonaws.com/assets.datacamp.com/production/course_1478/datasets/international.sav'

# Import international.sav as demo_1
demo_1 <- read.spss(path, to.data.frame=T)

# Print out the head of demo_1
head(demo_1)

# Import international.sav as demo_2
demo_2 <- read.spss(path, to.data.frame=T, use.value.labels=F)

# Print out the head of demo_2
head(demo_2)
str(demo_2)
```

